\chapter{Acknowledgements}

\textit{\small{I dedicate this to my father, who wished to do a PhD, but the
situation did not help him.}} 

\vspace{1cm}
I would like to appreciate my decision to do a PhD after years of being in the
industry . My first motivation was to
experience the educations in a mathematical environment. I was very pleased and
lucky to work with the best mathematicians in Norway
on the topic of CO$_2$ storage.

First and foremost, Knut-Andreas Lie was more than an adviser for me, whom I had
the chance and honor to work with closely and in a daily-based manner. I learned
a lot from discussions with Halvor M. Nilsen, initially my only friend in
Norway,
when I left my family and friends and moved to start the program. Jan
M. Nordbotten always inspired me and made me to love mathematics even more.
Helge Dahle warmly helped me with every aspect of my studies. Maria Elenius gave
me the enthusiasm as a colleague to enjoy my research. I enjoyed being an
office-mate at SINTEF with Christian Schulz. Arne Skorstad is among those whom
I was proud to work with. I was lucky to work with Princeton people, Michael
Celia and Sarah Gasda. I enjoyed learning from Ivar Aavatsmark, Hans
Munthe-Kaas, and Anette Stephansen. And many friends in Bergen Math.
department that I always enjoyed discussing interesting topics with them.

During this program I had the chance to spend one semester in Stuttgart to
work with mathematicians on stochastic analysis. I was proud to be sitting in
the group of Rainer Helmig, to enjoy time with such a live and friendly
research group. Thanks to Stuttgart people, one by one, for such a nice social
time that I had over there. I had very constructive scientific discussions with
Segrey
Oladyshkin and Wolfgang Nowak, Holger Class, and Anozie Ebigboe. I extremely
enjoyed working with them.

I would like to thank my manager at my new employer, Ed Leung, for supporting
me to finish my thesis.

And thanks to the coffee machine and printer at SINTEF-ICT, for helping me a lot
in writing this report.











